Reanalysis Step 7: Missingness Pattern Analysis

### 2025-09-01 reanalysis-7-missingness_patterns.qmd
fix ai idiiocy

# Based on the actual column names used in functions.R formulas
# Core demographic variables
demographic_vars <- c("age", "age_cat", "gender_cat", "race_ethnic_cat")

# Insurance and healthcare access
insurance_vars <- c("insurance_cat", "PCP_visits", "eye_visits")

# Diabetes-related variables
diabetes_vars <- c("insulin", "DCSI", "DM_duration")

# Comorbidity variables
comorbidity_vars <- c("CCI", "HTN", "dyslipidemia", "CVD", "CKD_stage")

# Vision-related variables
vision_vars <- c("baseline_VA_logMAR", "baseline_VA_cat", "dr_severity", 
                 "any_treatment", "DME")

# Treatment/exposure
exposure_var <- "ever_lapse_binary"

# Outcome variables
outcome_vars <- c("outcome_va_logMAR", "outcome_va_vi_binary")

# Combine all variables
all_vars <- c(demographic_vars, insurance_vars, diabetes_vars, 
              comorbidity_vars, vision_vars, exposure_var, outcome_vars)

@@

```{r descriptive-stats}
# Create Table 1 comparing excluded vs included
# Specify variable types (using actual column names from formulas)
factor_vars <- c("age_cat", "gender_cat", "race_ethnic_cat", "insurance_cat", 
                 "insulin", "HTN", "dyslipidemia", "CVD",
                 "CKD_stage", "baseline_VA_cat", "dr_severity", "any_treatment",
                 "DME", "ever_lapse_binary")

>>>>

# Variables from the actual matching and outcome formulas in functions.R
# Demographics created by load_and_prepare_data
demographic_vars <- c("age", "age_cat", "gender_cat", "race_ethnic_cat", "insurance_cat")

# Comorbidity scores (these ARE in the raw data)
comorbidity_vars <- c("CCI", "DCSI")

# Vision and treatment variables
vision_vars <- c("baseline_VA_logMAR")

# Treatment flags (these ARE in the raw data)
treatment_vars <- c("other_inject", "anti_VEGF", "focal_laser_flag", "PRP_flag")

# Other eye conditions
eye_condition_vars <- c("glaucoma_bef_hitplus_cat", "otherretina_bef_hitplus_cat", 
                        "catsurg_before_hitplus_cat")

# DR severity (created by the function)
dr_vars <- c("dr_severity")

# Treatment/exposure (created by the function)
exposure_var <- "ever_lapse_binary"

# Outcome variables (created by the function)
outcome_vars <- c("outcome_va_logMAR", "outcome_va_vi_binary")

# Combine all variables
all_vars <- c(demographic_vars, comorbidity_vars, vision_vars, treatment_vars,
              eye_condition_vars, dr_vars, exposure_var, outcome_vars)

@@

```{r descriptive-stats}
# Create Table 1 comparing excluded vs included
# Specify which variables should be treated as factors
factor_vars <- c("age_cat", "gender_cat", "race_ethnic_cat", "insurance_cat",
                 "glaucoma_bef_hitplus_cat", "otherretina_bef_hitplus_cat", 
                 "catsurg_before_hitplus_cat", "dr_severity", "ever_lapse_binary")
